Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-13 Ben_Manuscripts/thesis/transport.tex
Added missing intro figs

  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
  1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

@@

  Of the two diols, ethylene glycol moves significantly faster than propylene
  glycol due to propylene glycol's affinity for the monomer head groups.
  Combined with an increase in size, the addition of a single methyl group to
  ethylene glycol increases propylene glycol's hydrophobic character and causes
  it to favor positions near monomer head groups (see Figure~\ref{fig:polyols_rdf}).
  Both diols have comparable densities close to the pore center, however propylene
  glycol's density has a large peak near the monomer head groups relative to 
  ethylene glycol. Propylene glycol can form more highly stabilized hydrogen 
  bonds with carboxylate groups, explaining the slightly higher incidence of 
  hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}. The 95\textsuperscript{th}
  percentile of hydrogen bond lifetimes for propylene glycol with monomers is 
  9.5 ns compared to 7 ns for ethylene glycol. Somewhat counterintuitively, there is a 
  relatively high density of ethylene glycol molecules beyond the head group region
  probably due to its relatively small size. This likely contributes to the somewhat
  large error bars on its MSD in Figure~\ref{fig:msds}.

@@

  DMSO has a comparable MSD to acetone even though it is a larger molecule
  (see Figure~\ref{fig:msds}). DMSO spends 17\% more time in the pore than acetone. 
  On average, 35\% of DMSO molecules are coordinated to a sodium ion each
  frame compared with 26\% of acetone molecules. The pyramidal structure 
  of DMSO may force it to spend more time closer to the pore center which
  increases its interaction with sodium ions. The tendency of DMSO to stay
  in the pore region counterbalances the sodium ion interactions to give it
  a higher MSD than acetone.

>>>>

  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
  1 $\mu$s MD simulations using 
  Equation~\ref{eqn:ta_msd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:ta_msd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form1}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form1}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds2}
  \end{figure}

@@

  Of the two diols, ethylene glycol moves significantly faster than propylene
  glycol due to propylene glycol's affinity for the monomer head groups.
  Combined with an increase in size, the addition of a single methyl group to
  ethylene glycol increases propylene glycol's hydrophobic character and causes
  it to favor positions near monomer head groups (see Figure~\ref{fig:polyols_rdf}).
  Both diols have comparable densities close to the pore center, however propylene
  glycol's density has a large peak near the monomer head groups relative to 
  ethylene glycol. Propylene glycol can form more highly stabilized hydrogen 
  bonds with carboxylate groups, explaining the slightly higher incidence of 
  hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}. The 95\textsuperscript{th}
  percentile of hydrogen bond lifetimes for propylene glycol with monomers is 
  9.5 ns compared to 7 ns for ethylene glycol. Somewhat counterintuitively, there is a 
  relatively high density of ethylene glycol molecules beyond the head group region
  probably due to its relatively small size. This likely contributes to the somewhat
  large error bars on its MSD in Figure~\ref{fig:msds2}.

@@

  DMSO has a comparable MSD to acetone even though it is a larger molecule
  (see Figure~\ref{fig:msds2}). DMSO spends 17\% more time in the pore than acetone. 
  On average, 35\% of DMSO molecules are coordinated to a sodium ion each
  frame compared with 26\% of acetone molecules. The pyramidal structure 
  of DMSO may force it to spend more time closer to the pore center which
  increases its interaction with sodium ions. The tendency of DMSO to stay
  in the pore region counterbalances the sodium ion interactions to give it
  a higher MSD than acetone.
